---
title: "Clatherate Formation Data Lab 5"
author: "A.Mayuri(2348133)"
date: "2023-12-08"
output: word_document
---
## Problem Statement:

1. Fit a suitable linear regression model. 

2. Construct a normal probability plot of the residuals. Does there seem to be any problem with the normality and constant variance assumption?If yes, what remedial measure will u perform?

3. Construct and interpret a plot of the residuals.

4. Are the residuals correlated?

5. Is multicollinearity a potential problem in your model? If it is a problem, what is your remedy?

6. Are there any outliers in the data? If it exists, how will you treat it?



## Import Dataset
```{r}
library(readxl)
Chem <- read_excel("C:/Users/mayur/Desktop/Mstat/Semesters/Tri-sem2/Regression/Dataset/Chem.xlsx")
View(Chem)
attach(Chem)

```
### 1) Understanding the Variables Using correlation

```{r}
cor(Chem)
```

We observe that there is a positive linear relation between the independent and dependent variable ie, (X1,Y) AND (X2,Y). Also there is a very low correlation between (X1,X2). Hence they are independent to each other. 

### 2) Fitting a Linear Regression Model
```{r}
model1=lm(Chem$y~.,data = Chem)
model1
summary(model1)
```
We observe that both the independent variables have a significant linear relationship. since the values of both the independent variables are <=0.05 we reject null hypothesis and accept alternative hypothesis.ie, there exisist a linear relationship between parameter and dependent variable.




### 3) Residual Analysis (Question3)
```{r}
fit1=fitted.values(model1)
fit1

# Residual analysis 
plot(fit1,resid(model1))
abline(0,0)
plot(fit1,rstandard(model1))#standardized residual model
abline(0,0)
plot(fit1,rstudent(model1))# studentized residual model
abline(0,0)

## Residual values
residual=resid(model1)
residual


```

Using standard and studentized residual plot we observe that there is no pattern hence we cannot comment about both the assumption . 
we will further check it by using the test.

### 4a)Normality (Question2) and Variance
```{r}
# to check for res vales (Normality check)
re1=rstandard(model1)
re1


plot(model1)
shapiro.test(re1)
```

For Normality assumption using Shapiro Wilk Test
at 0.05 level of significance the p value>=0.05 thus we fail to reject null thus the residual follow normal distribution hence the assumption of errors. This is also confirmed using the QQ residual plot

### 4b) Hypothesis testing for constant variance using BP test :
test for errors have constant variance through errors. use the fitted model.

h0: error have const variance
h1: error have not const variance

```{r}
library(lmtest)
bptest(model1)

```
since p-value is <=0.05 we reject h0 ,thus there is no constant variance . hence the assumption of constant variance is not validated .
we can perform a log transformation to the dependent variable and try to redefine the model.


### 5a) Autocorrelation (question4)
```{r}
acf(residual)
```
ACF at 0 is always 1. and all acf points are not within the threshold lines from lag 1 it indicates that there is a significant autocorrelation among the residual series. However we can also confirm the same with durbin watson test procdure.


#### b) Durbin watson for ACF

h0: rho=0 there is no autocorrelation
h1: rho=!0 there is autocorrelation

```{r}
dwtest(model1)
```
at 5 % level of significance, the p value (6.004e-06)<0.05, we reject the null hypothesis that there is a  significant auto-correlation.
ie,rho=!=0.


### 6)Multi-collilinearity  (Question5):
We observe that the there could be no multi-collilinearity between independent variable since the correlation between them is (-0.12)<0.7. hence their VIF would be less than 5.

For confirmation,

```{r}
library(car)
vif(model1)

```
As stated the VIF<=5 thus there is no multi-collilinearity.



### 7)Outliers (Question6)
```{r}

rstandard(model1)
```

Here we observe that there is no observation below -3 and above 3. hence there are no outliers.



```{r}

```




