---
title: "non-linear regression"
author: "A.Mayuri(2348133)"
date: "2024-01-12"
output: word_document
---

question:

The below data represents the  substrate concentration (S) and the observed velocity (v) based on an enzymology experiment. 

Fit a non linear regression model that relates velocity to concentration using Michaelis-Menten equation .

Analyse and examine whether you can fit a simple linear regression model that relates velocity and substrate concentration by using any suitable transformation.


## Import dataset


```{r }
library(readxl)
rate <- read_excel("C:/Users/mayur/Desktop/Mstat/Semesters/Tri-sem2/Regression/Dataset/rate.xlsx")
View(rate)
attach(rate)
```

```{r }
plot(rate$S,rate$V,col="hotpink",xlab="concentration",ylab="Velocity",main="substrate concentration and velocity")


```


```{r }

model1=nls(V~Vmax*S/(k_m+S),start=c(Vmax=72,k_m=5),data=rate)
model1

```



```{r }
summary(model1)
```

the value for k and v_max values are not zero and hence a significant value. r^2 not a good metric to study the fit since x and y are not linear . thus the value of v_max is 73.26 and k_m is 3.43


```{r }
confint(model1)
```
95% of the time the true value will lie within this range

Vmax 63.302914 84.889668
k_m   1.958589  5.794501


```{r }
plot(S,V,xlab="Concentration", ylab="Velocity")
lines(S,predict(model1))
summary(model1)
plot(resid(model1))
```


```{r }
resid(model1)
```

## normality 

```{r }
shapiro.test((resid(model1)))
qqnorm(resid(model1))
qqline(resid(model1))
```

since the p value is greater than alpha(0.05) thus it forllows normality condition.


## Transformation to linear model.


To perform linear regression, we
need to have a function of V be linearly related to a function of [S]. This is achieved
via taking the reciprocal of both sides of this equation.


```{r }
library(readxl)
rate1 <- read_excel("C:/Users/mayur/Desktop/Mstat/Semesters/Tri-sem2/Regression/Dataset/rate1.xlsx")
View(rate1)
attach(rate1)
```



```{r }

S_inv=1/(s)
V_inv=1/(v)
plot(S_inv,V_inv)
model2=lm(V_inv~S_inv)
model2


```






```{r }
summary(model2)
```

# Normality and constant variance


```{r }
shapiro.test(resid(model2))
library(lmtest)
bptest(model2)
```

since for both p values are greater than alpha we accept null hypothesis and say that it follows normal distribution and has constant variance


Autocorrellation:

## Durbin watson for ACF

h0: rho=0 there is no autocorrelation
h1: rho=!0 there is autocorrelation
```{r }
dwtest(model2)
```
Since the pvalue is greater than alpha we fail to reject null hypothesis and conclude that there exsist no auto-correlation.
