---
title: "Weight Vs Systolic Blood Pressure"
author: "A.Mayuri(2348133)"
date: "2023-11-03"
output: word_document
---
# Question: The weight and systolic blood pressure of 26 randomly selected
males in the age group 25–30 are shown below.

##To Complete:
1. Obtain the scatter plot and interpret it.
2. Find a regression line connecting the variables systolic pressure and
weight. Interpret the plot, intercept term and regression coefficients.What
do you infer from the sign of regression coefficient?
3. Obtain the fitted values. Does the sum of fitted values is equal to the sum
of observed values ?

Based on the above questions, prepare a report with introduction, analysis and
conclusions.

###Introduction: 
We are given a dataset of size 26 and this encloses adults of age 25-30. we are given information about their respective weights and systolic BP. 

###Variables of Interest:
the independent (x) variable is that of the adults weight in pounds and the dependent (y) variable is their systolic BP in mmHg. 

      


## Step1 : Import Dataset 
```{r}
library(readxl)
Lab11 <- read_excel("C:/Users/mayur/Desktop/Mstat/Semesters/Tri-sem2/Regression/Dataset/Lab11.xlsx")
View(Lab11)
attach(Lab11)
```


## Step2 : Scatter Plot
```{r}
plot(Lab11$Weight,Lab11$`Symbolic BP`,col='green',main='Weight Vs Systolic BP',xlab='Weight in pounds',ylab = 'Systolic BP in mmHg')
```
Observation: We observer that there exist a positive linear relation between the 2 variables of interest now we will try to understand the magnitude of the same relationship.

## Step3: Correlation
```{r}
cor(Lab11$Weight,Lab11$`Symbolic BP`)
```
Observation:The correlation coefficient between the two variables is obtained as 0.7734 which is <0.8. Hence the variables have a moderately positive correlation between them.

## Step4: Model

```{r}

model=lm(Lab11$`Symbolic BP`~Lab11$Weight)
summary(model)
```
Interpretation: if Y=B1+B2(x) is the model, then from the above table we observe that 69.10437 is the intercept and the B2 value(slope value) is 0.41942. ie, for a unit change in weight there will be 0.41942 mmHg change in BP.
Also the positive B2 (Cov(x,y)/Sd(x)*Sd(y)) value shows that there is a positive relationship between the independent variable and the dependent variable.Since the only way for B2 to be positive is when cov(x,y) is positive. 

## Step5: Fitting Model

```{r}

Fit=fitted.values(model)
Fit
```
## Step6 : Fitted Values VS Observed Values
```{r}
plot(Lab11$Weight,Lab11$`Symbolic BP`)
scatter.smooth(Lab11$Weight,Lab11$`Symbolic BP`,col='blue')
#using the abline command
abline(lm(Lab11$`Symbolic BP`~Lab11$Weight))
```
Interpretation :
The graph above is the best possible fit for the given data set. It has minimized that sum of square of errors for the observed data set.ie the independent variable - the systolic Blood pressure.




## Step7 : To Verify if sum of observed value equals Fitted Values.
```{r}
M=data.frame(Fit)
M
sum(M)

sum(Lab11$`Symbolic BP`)
```
Here we observe that the sum of systolic pressure under fitted values is same as the observed/recorded values. Hence verified.

# Conclusion: 
From the above exercise we can conclude the following
there is a moderate linear positive relationship between weight and systolic BP.

With a correlation coefficient of 0.77. 

The model is of the form : 
y=B1+B2*X 
where 
B1=69.10437
B2=0.41942

The positive sign of B2 in an indication that the variables have a positive relationship.

ie, an increase in weight can be  associated and can lead to Blood pressure issues. On the contrary there are times where chronic increase in blood pressure due to lack of iodine/salt can push up the weight of a person significantly. this can also be verified by clinical analysis along with regression analysis.
